{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-30 brains-protocol.tex
Emphasize that all figures show a single attractor

\medskip
Results are gathered on Fig.~\ref{fig:feature-variations}.
We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1.
In other words, each feature exhibits a unique attractor.  
Second, the comparison with $\mathcal{H}_0$ shows that there are two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$) or (ii) $\nu_{\phi}$ remains always above or below $\nu_{\phi}^0$.

@@

\rk{Also, the figures make sense together: they \emph{all} show a single attractor, so mas alla de las differences between each feature, we see attraction.}

>>>>

\medskip
Results are gathered on Fig.~\ref{fig:feature-variations}.
We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1, independently of the feature considered.
In other words, each feature exhibits a unique attractor beyond its own particular variation patterns.
Second, the comparison with $\mathcal{H}_0$ shows that there are two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$) or (ii) $\nu_{\phi}$ remains always above or below $\nu_{\phi}^0$.

@@
